---
title: "FANCY PLOTS with Plotly"
author: "Karthik Theivendran"
date: "June 19, 2018"
output: 
  ioslides_presentation: 
    keep_md: yes
---

##Introduction


* Creating a web page presentation using R Markdown that features a plot created with Plotly.


* This presentaion includes 2 different plots with code attached, where i'm trying to show the real benefit of using "Plotly" package.

```{r inti, eval=TRUE}
#install.packages("plotly")
library(plotly)

```

##Mtcars 3D plot

```{r plot1, echo=TRUE, eval=FALSE}

data("mtcars") ##attaching required data

##re-evaluating [am] parameter and factoring it
mtcars$am[which(mtcars$am == 0)] <- 'Automatic'
mtcars$am[which(mtcars$am == 1)] <- 'Manual'
mtcars$am <- as.factor(mtcars$am)

p <- plot_ly(mtcars, x = ~wt, y = ~hp,
             z = ~qsec, color = ~am,
             colors = c('#BF382A',
                        '#0C4B8E')) %>%
    add_markers() %>% 
    layout(scene = list(
        xaxis = list(title = 'Weight'),
        yaxis = list(title = 'Gross horsepower'),
        zaxis = list(title = '1/4 mile time'))); p
```

##Mtcars 3D plot [continue]

```{r plot1_show, echo=FALSE,eval = TRUE}

data("mtcars")

mtcars$am[which(mtcars$am == 0)] <- 'Automatic'
mtcars$am[which(mtcars$am == 1)] <- 'Manual'
mtcars$am <- as.factor(mtcars$am)

p <- plot_ly(mtcars, x = ~wt, y = ~hp, z = ~qsec, color = ~am, colors = c('#BF382A', '#0C4B8E')) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'Weight'),
                     yaxis = list(title = 'Gross horsepower'),
                     zaxis = list(title = '1/4 mile time'))); p
```

##Life Expectancy and GDP

```{r LE+GDP, echo=TRUE, eval=FALSE}

#downloading data
data <- read.csv("https://raw.githubusercontent.com/plotly
                 /datasets/master/gapminderDataFiveYear.csv")

#subsetting the data
data_2007 <- data[which(data$year == 2007), ]
#ordering based on 2 parameters
data_2007 <- data_2007[order(data_2007$continent, 
                             data_2007$country),] 
slope <- 2.666051223553066e-05
#defining bubble's based on population size
data_2007$size <- sqrt(data_2007$pop * slope) 
#definig colors variable
colors <- c('#4AC6B7', '#1972A4', '#965F8A', '#FF7070', '#C61951') 

```


##Life Expectancy and GDP [continue]

```{r LE+GDP2, echo=TRUE, eval=FALSE}
p <- plot_ly(data_2007, x = ~gdpPercap, y = ~lifeExp, color = ~continent,
             size = ~size, colors = colors,type = 'scatter', mode = 'markers', 
             sizes = c(min(data_2007$size), max(data_2007$size)),
             marker = list(symbol = 'circle', sizemode = 'diameter',
                           line = list(width = 2, color = '#FFFFFF')),
             text = ~paste('Country:', country, '<br>Life Expectancy:', lifeExp,
                           '<br>GDP:', gdpPercap,'<br>Pop.:', pop)) %>%
    layout(title = 'Life Expectancy v. Per Capita GDP, 2007',
           xaxis = list(title = 'GDP per capita (2000 dollars)',
                        gridcolor = 'rgb(255, 255, 255)',
                        range = c(2.003297660701705, 5.191505530708712),
                        type = 'log', zerolinewidth = 1, ticklen = 5, gridwidth = 2),
           yaxis = list(title = 'Life Expectancy (years)', gridcolor = 'rgb(255, 255, 255)',
                        range = c(36.12621671352166, 91.72921793264332),
                        zerolinewidth = 1, ticklen = 5, gridwith = 2),
           paper_bgcolor = 'rgb(243, 243, 243)',
           plot_bgcolor = 'rgb(243, 243, 243)')
```


##Life Expectancy and GDP [continue]
```{r LE+GDP3, echo=FALSE, eval=TRUE}

#downloading data
data <- read.csv("https://raw.githubusercontent.com/plotly
                 /datasets/master/gapminderDataFiveYear.csv")

#subsetting the data
data_2007 <- data[which(data$year == 2007), ]
#ordering based on 2 parameters
data_2007 <- data_2007[order(data_2007$continent, 
                             data_2007$country),] 
slope <- 2.666051223553066e-05
#defining bubble's based on population size
data_2007$size <- sqrt(data_2007$pop * slope) 
#definig colors variable
colors <- c('#4AC6B7', '#1972A4', '#965F8A', '#FF7070', '#C61951') 

p <- plot_ly(data_2007, x = ~gdpPercap, y = ~lifeExp, color = ~continent,
             size = ~size, colors = colors,type = 'scatter', mode = 'markers', 
             sizes = c(min(data_2007$size), max(data_2007$size)),
             marker = list(symbol = 'circle', sizemode = 'diameter',
                           line = list(width = 2, color = '#FFFFFF')),
             text = ~paste('Country:', country, '<br>Life Expectancy:', lifeExp,
                           '<br>GDP:', gdpPercap,'<br>Pop.:', pop)) %>%
    layout(title = 'Life Expectancy v. Per Capita GDP, 2007',
           xaxis = list(title = 'GDP per capita (2000 dollars)',
                        gridcolor = 'rgb(255, 255, 255)',
                        range = c(2.003297660701705, 5.191505530708712),
                        type = 'log', zerolinewidth = 1, ticklen = 5, gridwidth = 2),
           yaxis = list(title = 'Life Expectancy (years)', gridcolor = 'rgb(255, 255, 255)',
                        range = c(36.12621671352166, 91.72921793264332),
                        zerolinewidth = 1, ticklen = 5, gridwith = 2),
           paper_bgcolor = 'rgb(243, 243, 243)',
           plot_bgcolor = 'rgb(243, 243, 243)')
p

```


##Refrences

*Find various 3D charts at [here](https://goo.gl/Kb6ASp)

*Find fancy bubble charts at [here](https://goo.gl/bjvTdz)



**THANK YOU**
